Quality Definitions of Qualities

### 2019-11-07 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
changes defn robustness and performance

Definition \ref{RobustnessDefnSelected} rephrased: Software possesses the
characteristic of robustness if it fulfills its requirements correctly or
behaves reasonably in circumstances not anticipated in the requirements
specification. \wss{I think we might want to separate the definition of
  robustness and correctness.  I'm thinking we just want the definition of
  robustness to be how the software behaves in unanticipated circumstances.}

@@

@@

\begin{defn}
The degree to which a system or component accomplishes its designated functions
within given constraints, such as speed, accuracy, or memory usage
\citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn} \label{PerformanceDefnSelected}
How well or how rapidly the system must perform specific functions. Performance
requirements encompass speed (database response times, for instance), throughput
( transactions per second), capacity (con-current usage loads), and timing (hard
real-time demands) \citep{wiegers2003softreq}.
\end{defn}
\begin{defn}
In software engineering we often equate performance with efficiency. A software
system is efficient if it uses computing resources economically
\citep{ghezzi1991fundamentals}.
\end{defn}

@@

Definition \ref{PerformanceDefnSelected}: How well or how rapidly the system
must perform specific functions. Performance requirements encompass speed
(database response times, for instance), throughput ( transactions per second),
capacity (con-current usage loads), and timing (hard real-time demands).

>>>>

Definition \ref{RobustnessDefnSelected} rephrased: Software possesses the
characteristic of robustness if it behaves ``reasonably'' in circumstances that were not anticipated in the requirements specification or are in violation of it.

@@

\pmi{Still want to refine what we mean by reasonable}

@@

\begin{defn} \label{PerformanceDefnSelected}
The degree to which a system or component accomplishes its designated functions
within given constraints, such as speed, accuracy, or memory usage
\citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn} \label{PerformanceDefnSelected2}
How well or how rapidly the system must perform specific functions. Performance
requirements encompass speed (database response times, for instance), throughput
( transactions per second), capacity (con-current usage loads), and timing (hard
real-time demands) \citep{wiegers2003softreq}.
\end{defn}
\begin{defn}
In software engineering we often equate performance with efficiency. A software
system is efficient if it uses computing resources economically
\citep{ghezzi1991fundamentals}.
\end{defn}

@@

Combined definition \ref{PerformanceDefnSelected} and \ref{PerformanceDefnSelected2}: The degree to which a system or component accomplishes its designated functions within given constraints, such as speed
(database response times, for instance), throughput ( transactions per second),
capacity (con-current usage loads), and timing (hard real-time demands).
